---
title: "hongple_v0.5"
author: "Joel Lee"
date: "2015. 9. 16."
output: html_document
---
---
output:
html_document:
toc: yes
---

##### 초기화 및 대화형 임팔라 접속  
```{r load, echo=FALSE, results='hide'}

# install.packages("Hmisc")
# install.packages("RODBC")
# install.packages("sqldf")
# install.packages('ggplot2')
# install.packages("psych")
# install.packages("rmarkdown")
# install.packages("cluster")
# install.packages("fpc")

library("Hmisc")
library("rmarkdown")
library("RODBC")
library("sqldf")
library(ggplot2)
library("psych")
library(cluster)
library(fpc)
library(xtable)
```

```{r echo=FALSE}
setwd("~/workspace/hongple")
rm(list = ls())  # clear objects  
source("executeSQL.R")
print_desc <- function(df){
    xt <- xtable(describe(df))
    print(xt, type="html")
}

print_summary <- function(df){
 #   df$ro_y <- sapply(df$ro_y, as.factor)
 #   df$ceq_rgst_dt <- sapply(df$ceq_rgst_dt, as.factor)

    xt <- xtable(summary(df))
    print(xt, type="html")
}
```

#### 주요 영향요인(센서) 분석  

# 샘플링 표준편차 = 0 인 센서
6 ems16_pre_fuel_cut_in, C 
8 ems16_soak_time_error, C
10 ems16_spk_time_cur, A, 연속형              
24 fatc11_cf_fatc_autoactivation, C
28 ems_h12_cf_cdastat, A              
30 ems_h12_cf_ems_oilchg, C           
31 ems_h12_cf_ems_etclimpmod, A
-- 33 ems_h12_cf_ems_uptargr, C          
-- 34 ems_h12_cf_ems_downtargr, C        
36 ems_h12_cf_ems_hpresstat, B        
37 ems_h12_cf_ems_fcopen, C           
59 esp12_cyl_press_diag, C
69 tcu12_fuel_cut_tcu, A              
71 tcu12_idle_up_tcu, A 
73 tcu12_spk_rtd_tcu, A
76 ems11_f_n_eng, C, X                   
79 ems11_tq_cor_stat, C, X
81 ems11_f_sub_tqi, C, X                 
89 ems15_qecacc, C                    
90 ems15_ecfail, B                    
91 ems15_fa_pv_can, B                 
93 ems15_state_dc_obd, C              
94 ems15_inh_dc_obd, C                
95 ems15_ctr_ig_cyc_obd, C, 연속형
96 ems15_ctr_cdn_obd, C, 연속형    
97 ems14_im_autehn, B                 
102 tcu13_cf_tcu_inhcda, A
112 ems12_vb_off_act, A              

샘플 데이터 가져오기
```{r qplot, fig.height=3, fig.width=6, cache=TRUE}
# 실제값
df_sample = data.frame(executeSql("select * from vcrm_6442267.rg_log_um_f_rare"))
test_df <- df_sample[,c(-1:-4)]
test_df <- test_df[,c(-6,-8,-10,-24,-28,-30,-31,-36,-37,-59,-69,-71,-73,-76,-79,-81,-89:-91,-93:-97,-102,-112)]
test_df <- test_df[,c(-12,-20,-34,-37,-44,-47,-52,-60,-76,-83,-88)]
test_df <- na.omit(test_df)
test_mat <- as.matrix(test_df)
test_mat_s <- scale(test_mat)
describe(test_df)

# 기초 통계
test_df_desc <- describe(test_df)
#print_desc(test_df)
#summary(test_df)

# 범주화값
df_sample2 = data.frame(executeSql("select * from vcrm_6442267.rg_log_um_f16_random"))
test_df2 <- df_sample2[,c(-1:-4)]
test_set <- test_df2[test_df2$cnt==1,]
test_set <- test_set[,c(-1,-2)]
test_set <- test_set[,c(-6,-8,-10,-24,-28,-30,-31,-36,-37,-59,-69,-71,-73,-76,-79,-81,-89:-91,-93:-97,-102,-112)]
test_set <- na.omit(test_set)
test_set_desc <- describe(test_set)
test_set <- test_set[,c(-12, -20, -34, -37, -44, -47, -52, -60, -76, -83, -86, -88)]
```
 


**DTC 데이터 분석**
```{r}

# 데이터 처리
dtc_df = data.frame(executeSql("select * from vcrm_6442267.dtc_rt_mnt_um_id where bkdw_cd like 'P%'"))
dtc_df <- dtc_df[,c(-1:-9)]
#dtc_desc <- describe(dtc_df)
dtc_df_f <- dtc_df[,c(-6,-8,-10,-15,-18,-23,-24,-28,-30,-31,-36,-37,-54,-56,-57,-61,-64,-66,-72,-77,-87,-89)]
dtc_df_f <- na.omit(dtc_df_f)
#f <- describe(dtc_df_f)
dtc_mat <- as.matrix(dtc_df_f)
dtc_mat_s <- scale(dtc_mat)

```


**요인 분석(Factor Analysis)**
```{r}
#fa.parallel(test_mat_s)
#Parallel analysis suggests that the number of factors =  24  and the number of components =  22 

#cor_mat <- cor(test_set, use="complete.obs")
#cov_mat <- cov(test_set, use="complete.obs")

fa.parallel(dtc_mat_s)
# Parallel analysis suggests that the number of factors =  21  and the number of components =  19 

fit <- fa(dtc_mat_s, nfactors=21)
#fa.graph(fit)
fa.diagram(fit)
plot(fit)

# fit2 <- factanal(dtc_mat_s, factors=20, rotation="varimax")
# fit2

```

```{r factor, fig.height=4, fig.width=6}
load <- fit$loadings[,1:16] 
plot(load,type="n") # set up plot 
text(load,labels=names(dtc_df_f),cex=.7)
```


**상관 분석**
```{r}

#시각화
#library(corrgram)
#corrgram(test_df, order=TRUE, lower.panel=panel.shade, upper.panel=panel.pie, text.panel=panel.txt,
#  main="EMS12 Data Correlation")

# Correlations with significance levels

# cor_result <- rcorr(test_mat)

# ++++++++++++++++++++++++++++
# flattenCorrMatrix
# ++++++++++++++++++++++++++++
# cormat : matrix of the correlation coefficients
# pmat : matrix of the correlation p-values
# flattenCorrMatrix <- function(cormat, pmat) {
#   ut <- upper.tri(cormat)
#   data.frame(
#     row = rownames(cormat)[row(cormat)[ut]],
#     column = rownames(cormat)[col(cormat)[ut]],
#     cor  =(cormat)[ut],
#     p = pmat[ut]
#     )
# }
# cor_result2 <- flattenCorrMatrix(cor_result$r, cor_result$P)

cor_result3 <- cor(dtc_df_f, use = "complete.obs")
#remove <- "tcu12_spk_rtd_tcu"
#cor_result3 <- cor_result3[!rownames(cor_result3) %in% remove,!colnames(cor_result3) %in% remove]

#symnum_result <- symnum(cor_result3)
#write.table(symnum_result, "mydata.csv", sep=",")

# install.packages("corrplot")
# library(corrplot)
corrplot(cor_result3, is.corr = FALSE, type="lower", order="hclust", tl.col="black", tl.srt=45)

```


**주성분 분석(PCA)**
```{r pca, fig.height=8, fig.width=8}

#graphics.off() 
#layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
# 표준편차 0이 아닌 센서만 선별

#test_df <- sensors[,c(1,4,6,8,9,10,11,12)]
pca = prcomp(dtc_mat, scale=TRUE, retx=TRUE)
#round(predict(pca),2)
#png("sensors_pca.png")
plot(pca, type="l", sub = "Scree Plot")
biplot(pca)
#dev.off()

```


**회귀 분석**
```{r}
dtc_f10 = data.frame(executeSql("select * from vcrm_6442267.dtc_rt_mnt_um_id_47_f10 where bkdw_cd like 'P%'"))

dtc_f10 = data.frame(executeSql("select * from vcrm_6442267.dtc_rt_mnt_um_id_47_f10 where bkdw_cd like 'P%'"))

a <- dtc_f10[,3]
b <- dtc_f10[,c(-1:-9,-104)]
c <- cbind(b,a)
names(c)[95] <- "bkdw_cd"

dtc_f10_f <- c[,c(-6,-8,-10,-15,-18,-23,-24,-28,-30,-31,-36,-37,-54,-56,-57,-61,-64,-66,-72,-77,-87,-89)]
dtc_f10_f <- na.omit(dtc_f10_f)

dtc_f10_f$flag <- NA
dtc_f10_f[dtc_f10_f$bkdw_cd == 'P2271',]$flag <- 1;
dtc_f10_f[dtc_f10_f$bkdw_cd != 'P2271',]$flag <- 0;

dtc_f10_f[dtc_f10_f$bkdw_cd == 'P2196',]$flag <- 1;
dtc_f10_f[dtc_f10_f$bkdw_cd != 'P2196',]$flag <- 0;

dtc_f10_f[dtc_f10_f$bkdw_cd == 'P0299',]$flag <- 1;
dtc_f10_f[dtc_f10_f$bkdw_cd != 'P0299',]$flag <- 0;

dtc_f10_f[dtc_f10_f$bkdw_cd == 'P242D',]$flag <- 1;
dtc_f10_f[dtc_f10_f$bkdw_cd != 'P242D',]$flag <- 0;

dtc_f10_f[dtc_f10_f$bkdw_cd == 'P0192',]$flag <- 1;
dtc_f10_f[dtc_f10_f$bkdw_cd != 'P0192',]$flag <- 0;

dtc_desc <- describe(dtc_f10_f)

#dtc_f10_f <- subset(dtc_f10_f, grepl("^P", dtc_f10_f$bkdw_cd), drop=FALSE)
test_set <- dtc_f10_f[,c(-7,-8,-12,-13,-17,-23:-25,-28,-29,-33,-35,-39,-42,-46,-54,-57,-64,-71)]

fmla <- as.formula(paste("flag ~ ", paste(names(test_set[,c(1:53)]),collapse="+")))
g = glm(fmla, data = test_set, family = binomial(link = "logit"))
summary(g) # display results
#P2271 <- g
#P0299 <- g

confint(g) # 95% CI for the coefficients
exp(coef(g)) # exponentiated coefficients
exp(confint(g)) # 95% CI for exponentiated coefficients
predict(g, type="response") # predicted values
residuals(g, type="deviance") # residuals
#coefficients(g)
#anova(g)
# diagnostic plots 
#graphics.off() 
#layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
#plot(g)
```


**군집 분석**
```{r}
# k-means
cl_result <- kmeans(test_df, iter.max = 1000, centers = 3)
# DBSCAN
cl_result <- dbscan(test_df, eps=2, MinPts=5)
#plotcluster(test_df, km_result$cluster)
clusplot(test_df, cl_result$cluster, color=TRUE, shade=TRUE, labels=2, lines=0)

# hierachical 
source("myfunctions.R")
d <- dist(test_df, method = "euclidean") # distance matrix
hc <- hclust(d, method="ward.D")
plot(hc) # display dendogram
groups <- cutree(hc, k=4) # cut tree into 5 clusters
# draw dendogram with red borders around the 5 clusters 
rect.hclust(hc, k=4, border="red")
```


**주요센서 + RO**  
```{r results="asis"}
sensor_vin_ro = data.frame(sqlQuery( conn, "select * from vcrm_6442267.factor5_um_vin_ro_ads"))
print_summary(sensor_vin_ro)

g = lm(ro_cnt ~ vin + id, data = sensor_vin_ro)
summary(g)
coefficients(g)
#anova(g)
# diagnostic plots 
#graphics.off() 
#layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
#plot(g)

```




